Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters

### 2023-06-27 report/report.tex
feat: Dockerbuild & rework readme

@@

\section{Experiments}
To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland. When a description was only available in German, we translated it to English using the online translator DeepL. A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-a}. We conducted the data collection manually since company websites are generally structured very differently, making it complicated to extract such information automatically. Thus, building a scraping tool was out of this project's scope. To test our location recommendation feature, we created company descriptions using GPT-4.
To test the impact of providing additional features to the clustering pipeline, we also gathered the features industry, products, customer base, market positioning, and revenue for each company.

@@

\appendix
\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link! Update readme in repo!}
\begin{itemize}
	\item \textbf{Link to Code}: Provide the link to your code repository. You can use any service to host your code (Github, gdrive etc.). The code should be running, accessible and all of your work must be reproducible. In case your code is not accessible or not in a working state, relevant number of points will be deducted.   
	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
\end{itemize}

\subsection{Companies in our Dataset}
\label{sec:appendix-a}
We list the $50$ Saarland companies in our dataset:
\begin{itemize}
	\item ZF
	\item Saarstahl
	\item Dillinger
	\item Bosch
	\item Festo
	\item Ford
	\item Schaeffler
	\item Fresenius
	\item Wagner
	\item Villery\&Boch
	\item Michelin
	\item ThyssenKrupp
	\item Hager
	\item Purem
	\item SaarGummi
	\item VOIT
	\item Meiser
	\item SAP
	\item Nemak
	\item Peter Gross Bau
	\item OBG Group
	\item URSAPHARM
	\item Hörmann
	\item Kunzler
	\item Diehl Defence
	\item HYDAC
	\item Backes AG
	\item Karlsberg
	\item Globus
	\item Caritas
	\item Uni Saar
	\item Welocalize
	\item Möbel Martin
	\item IKK Südwest
	\item Dr. Theiss
	\item Unimed
	\item CosmosDirekt
	\item ORBIS
	\item eurodata
	\item energis
	\item CISPA
	\item Greencells
	\item Scheer
	\item Iqony Energies
	\item PLUSCARD
	\item IAS Software
	\item Ludwig Schokolade
	\item MAT Foundries
	\item Adient
	\item Schröder
\end{itemize}

@@

>>>>

% Multi-column list
\usepackage{multicol}

@@

\section{Experiments}
To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland. When a description was only available in German, we translated it to English using the online translator DeepL. A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-companies}. We conducted the data collection manually since company websites are generally structured very differently, making it complicated to extract such information automatically. Thus, building a scraping tool was out of this project's scope. To test our location recommendation feature, we created company descriptions using GPT-4.
To test the impact of providing additional features to the clustering pipeline, we also gathered the features industry, products, customer base, market positioning, and revenue for each company.

@@

\newpage
\appendix
\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link! Update readme in repo!}
\begin{itemize}
	\item \textbf{Link to Code}: Provide the link to your code repository. You can use any service to host your code (Github, gdrive etc.). The code should be running, accessible and all of your work must be reproducible. In case your code is not accessible or not in a working state, relevant number of points will be deducted.   
	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
\end{itemize}

@@

\subsection{Companies in our Dataset}
\label{sec:appendix-companies}

We list the $50$ Saarland companies in our dataset:
\begin{multicols}{2} \begin{itemize}
	\item ZF
	\item Saarstahl
	\item Dillinger
	\item Bosch
	\item Festo
	\item Ford
	\item Schaeffler
	\item Fresenius
	\item Wagner
	\item Villery\&Boch
	\item Michelin
	\item ThyssenKrupp
	\item Hager
	\item Purem
	\item SaarGummi
	\item VOIT
	\item Meiser
	\item SAP
	\item Nemak
	\item Peter Gross Bau
	\item OBG Group
	\item URSAPHARM
	\item Hörmann
	\item Kunzler
	\item Diehl Defence
	\item HYDAC
	\item Backes AG
	\item Karlsberg
	\item Globus
	\item Caritas
	\item Uni Saar
	\item Welocalize
	\item Möbel Martin
	\item IKK Südwest
	\item Dr. Theiss
	\item Unimed
	\item CosmosDirekt
	\item ORBIS
	\item eurodata
	\item energis
	\item CISPA
	\item Greencells
	\item Scheer
	\item Iqony Energies
	\item PLUSCARD
	\item IAS Software
	\item Ludwig Schokolade
	\item MAT Foundries
	\item Adient
	\item Schröder
\end{itemize}\end{multicols}
